---
title: "Homework 8"
author: "Fabián A. Araneda-Baltierra based on Kaveri Chhikara's TA"
date: "12/8/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
rm(list = ls())

# Load packages
library('rmutil')
library('tidyverse')
library('dplyr')
library('moments')
library('haven')
library('boot')
# Set a seed for random calculations
set.seed(11221111)
```

**Question 3**
First, we load data and data cleaning
```{r}
data <- data.frame(read_dta("Homework_8.dta"))
```


The data file has seven variables. "treated" indicates whether an individual is in the treatment group or the control group. "work" to identify whether the individual is working or not. 

```{r}
y_treat <- lm(work ~ treated, data)
summary(y_treat)
```

The treatment effect is the coefficient from the linear regression, which is 0.07794
The value 0.07794 indicates the fraction of people who benefit by being part of the treatment group where they received job search assistance. 


#marginals pmfs
**Question 3.A**
```{r}
f_treat <- data %>%  filter(treated == 1) %>% count(work)
f_treat %>%  mutate (prob = n/sum(n))

```
**Question 3.B**
```{r}
f_control <- data %>%  filter(treated == 0) %>% count(work)
f_control %>%  mutate (prob = n/sum(n))
```
